%-------------------------
% Resume in Latex
% Author : Kyle Earp
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\setlength{\footskip}{4.08003pt}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \textsc{Kyle Earp}} \\ \vspace{1pt}
    \small 254-462-8580 $|$ \href{mailto:kearp03@centurylink.net}{\underline{kearp03@centurylink.net}} $|$ \href{https://github.com/kearp03}{\underline{github.com/kearp03}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tarleton State University \textnormal{- GPA: 4.0}}{Stephenville, TX}
      {}{Aug. 2021 -- May 2025}
      \resumeItemListStart
        \resumeItem{B.S. in Mathematics, Concentration in Data Analysis}
        \resumeItem{B.S. in Computer Science, Concentration in Artificial Intelligence and Data Science}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Research Assistant}{May 2023 -- Present}
      {Tarleton State University}{Stephenville, TX}
      \resumeItemListStart
        \resumeItem{Contriubted to the development and optimization of various Python scripts and algorithms to analyze and visualize data, enhancing the accuracy and efficiency of data processing and interpretation.}
        \resumeItem{Collaborated with faculty and graduate students to design and implement research projects, conducting literature reviews and data analysis to support ongoing research initiatives.}
        \resumeItem{Conducted rigorous testing and debugging of simulation software, ensuring robust performance and reliability while documenting processes to facilitate knowledge transfer and future research initiatives.}
        \resumeItem{Presented research findings at academic conferences and seminars, engaging with peers and faculty to discuss results and solicit feedback to enhance research quality and impact.}
      \resumeItemListEnd

    \resumeSubheading
      {Mathematics Tutor}{January 2022 -- Present}
      {Tarleton State University}{Stephenville, TX}
      \resumeItemListStart
        \resumeItem{Assisted students in understanding complex mathematical concepts, providing guidance to enhance comprehension and academic performance.}
        \resumeItem{Recieved training in effective tutoring techniques and strategies, adapting to diverse learning styles and individual needs to maximize student success.}
        \resumeItem{Coordinated with other tutors and faculty to develop and implement innovative teaching methods, fostering a collaborative learning environment and promoting student engagement.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Bayesian Methods to Infer ODE Model Parameters} $|$ \emph{Python, Jupyter, Bash}}{January 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Adapted and implemented Bayesian inference methods to estimate parameters of ordinary differential equation (ODE) models, enhancing accuracy and robustness of parameter estimation in biological systems in relation to specific outbreaks.}
            \resumeItem{Utilized the Python library BayesFlow to impliment neural networks to estimate posterior distributions for parameter values and adapted the library to different disease models and outbreaks.}
            \resumeItem{Developed a Jupyter notebook to visualize the results of the Bayesian inference, enabling users to interact with the data and explore the impact of different parameters on the model.}
            \resumeItem{Automated the data processing and analysis pipeline using Bash scripts, streamlining the workflow and reducing the time required to generate results.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Musical Note Transposer with Interactive GUI} $|$ \emph{Python, Tkinter, Java}}{August 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a graphical interface to transpose musical notes, enabling users to input original and desired key signatures and display the transposed notes in real-time.}
            \resumeItem{Implemented the Tkinter library to create a user-friendly interface, allowing users to interact with the program and continually enter notes to transpose and change the original and desired keys.}
            \resumeItem{Develop verstions of the program in multiple languages to reinforce understanding of programming concepts and enhance versatility in software development.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, Java, Mathematica} \\
     \textbf{Developer Tools}{: Git, Visual Studio, Linux, VS Code} \\
     \textbf{Libraries}{: BayesFlow, Matplotlib, NumPy, Scipy, Pandas, Tkinter, CUDA} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
